### 2012-10-02 MSteenhagen-CV.tex
Added links. Some revision. Added date-stamp.

%% color for the links 
\usepackage{color}

%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

@@

\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics; Metaethics.

@@

\ind Metaphysics; History of Twentieth Century Philosophy; Political Philosophy.

@@

@@

\noindent\emph{University of Utrecht\vspace{0.02in}}

@@

\noindent\emph{ARTeZ School of Fine Art\vspace{0.02in}}

@@

\noindent\emph{Heythrop College London \vspace{0.01in}}

@@

\noindent\emph{University of Kent \vspace{0.01in}}

@@

@@

\noindent\emph{Utrecht School of Arts \vspace{0.01in}}

@@

\noindent\emph{University of Utrecht \vspace{0.01in}}

@@

\ind 2012. British Society of Aesthetics PhD Studentship Award. (£36.000)

@@

\ind 2012--Present. Editor of the \emph{Postgraduate Journal of Aesthetics.}

\ind 2010--Present. Co-Organiser London Aesthetics Forum, Institute of Philosophy, London.

\ind 2012--Present. Website Editor London Philosophy and Psychoanalysis Group.

\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (ESPP) Annual Conference 2012, Institute of Philosophy, London.

\ind 2011. UCL Representative for the British Postgraduate Philosophy Association.

\ind 2007-2009. Editor of \emph{Cimedart}, Philosophy Journal of the University of Amsterdam.

@@

% %% Publications

>>>>

%% color for the links 
\usepackage{color}
\definecolor{grey}{cmyk}{0,1,0,0.8}
%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=grey,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

@@

\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics.

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ Century Philosophy; Political Philosophy.

@@

\noindent\emph{University College London, Dept. Philosophy \vspace{0.01in}}

@@

\noindent\emph{University of Utrecht, Dept. Philosophy\vspace{0.02in}}

@@

\noindent\emph{ARTeZ School of Fine Art, Dept. Monumental Art\vspace{0.02in}}

@@

\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Dept. Philosophy} \vspace{0.01in}}

@@

\noindent\href{http://www.kent.ac.uk/arts/hpa/index.html}{\emph{University of Kent, History \amper Philosophy of Art} \vspace{0.01in}}

@@

\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Dept. Philosophy}} \vspace{0.01in}

@@

\noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}

@@

\noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}

@@

\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. (£36.000)

@@

\ind 2012--Present. Editor of the \href{http:\\www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics.}}

\ind 2010--Present. Co-Organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.

\ind 2012--Present. Website Editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.

\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (\href{http://www.eurospp.org}{ESPP}) Annual Conference 2012, Institute of Philosophy, London.

\ind 2011. UCL Representative for the \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association}.

\ind 2007-2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.

@@

\rfoot{\footnotesize{\today}}
% %% Publications
